Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-05 src/paper.tex
update

\subsubsection{Training sets}
We use the publicly available Kmeans tokenizer and scalable 
HiFi-GAN decoder in \cite{speechbrain}. The Kmeans tokenizer
is trained on \texttt{train\_clean\_100}, \texttt{train\_clean\_360}, and \texttt{train\_other\_500} of
LibriSpeech \cite{librispeech}, and the scalable HiFi-GAN is trained on \texttt{train\_clean\_100} of 
LibriTTS \cite{libritts}. The modeling stage is trained on 
\texttt{train\_clean\_100} and \texttt{train\_clean\_360} of LibriSpeech. All training data are 
generated on the fly with relative SNR between 0 dB to 5 dB.

>>>>

\subsubsection{Training}
We use the publicly available Kmeans tokenizer and scalable 
HiFi-GAN decoder in \cite{speechbrain}. The Kmeans tokenizer
is trained on \texttt{train\_clean\_100}, \texttt{train\_clean\_360}, and \texttt{train\_other\_500} of
LibriSpeech \cite{librispeech}, and the scalable HiFi-GAN is trained on \texttt{train\_clean\_100} of 
LibriTTS \cite{libritts}. The modeling stage is trained on 
\texttt{train\_clean\_100} and \texttt{train\_clean\_360} of LibriSpeech. All training data are 
generated on the fly with relative SNR between 0 dB to 5 dB. The mixture audio is segmented to 3 
seconds and the reference speech is segmented to 4 seconds. 
We use embedding dimension \(d=1024\) and

% \subsubsection{Test sets}
% We use the \texttt{dev} set of Libri2Mix \cite{librimix} to test our model performance and other baseline models.

% \subsubsection{Evaluation Metrics}
% As mentioned in studies
